Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-05-07 manuscript/manuscript.tex
addressed some things

\subsection{Power}
The power of the proposed test is investigated with data generated from
distributions that are not in the hypothesized distribution family. If the test
is indeed powerful, we would ideally want the probability of
rejecting $H_0$ when $H_0$ is false\jy{beta has been
  used. Discuss in terms of power: the probability of rejecting $H_0$ when $H_0$
  is false.}\mc{addressed}
to be 1, but we
expect it to be generally high. Again, we must try the method with different
marginal distributions to ensure that it is robust.
We would then expect the distribution of p-values to be non-uniform -
specifically a higher density of low p-values - and the 
rate \jy{Does not sound right. What is $\alpha$?}\mc{addressed}
of $\#(p_r < 0.05)$ - where 0.05 is the significance level - to be high,

@@

\jy{alpha has been used as gamma parameters. This is not necessary, Just say we
  checked the power when the significance level is .05.}\mc{addressed}
We can compute a rejection rate 
$q = \#\{p_r < 0.05\} / 1000$ for $r \in \{1, \ldots, 1000\}$.
Additionally, we can construct a 95\% confidence interval for 
this rate. Below are tables containing rejection rates showcasing the 
differences when simulation settings are changed.

@@

Using the \textsl{tseries} package  \citep{tseries}, 
we gathered daily closing prices for the S\&P 500 index from January 1st, 2020
to December 31st, 2023. Daily returns were obtained by taking the difference in
the logarithm of the closing prices.
Using our method, we tested that the daily returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
We tested the same hypotheses using \citet{babu2004goodness}'s 
non-parametric basic bootstrap bias correction and 
\citet{zeimbekakis2022misuses}'s parametric bootstrap method.
We used $B = 10,000$ bootstrap 
replicates in this analysis.
The p-values for these tests are highlighted in 
Table~\ref{table:SP5004}.

@@

\input{tables/sp100_pval_4y}

@@

The same analyses were repeated on the daily returns of the S\&P 100 index.
As shown in Table~\ref{table:SP1004}, 
our method demonstrates more instances where it reaches
different conclusions at the 0.05 significance level compared to other methods.
Our method does not reject the hypothesis that the series conforms to a
Student's $t$ distribution with degrees of freedom $v = 5$, yielding a p-value
of 0.0873. In contrast, \citet{babu2004goodness}'s method yields a p-value of 
0.0368, and \citet{zeimbekakis2022misuses}'s method yields a p-value of 0.03.
conclusions regarding the marginal distribution of the population under 
scrutiny.

>>>>

\subsection{Power}
The power of the proposed test is investigated with data generated from
distributions that are not in the hypothesized distribution family. If the test
is indeed powerful, we would ideally want the probability of
rejecting $H_0$ when $H_0$ is false\jy{beta has been
  used. Discuss in terms of power: the probability of rejecting $H_0$ when $H_0$
  is false.}\mc{addressed}
to be 1, but we
expect it to be generally high. Again, we must try the method with different
marginal distributions to ensure that it is robust.

@@

\jy{alpha has been used as gamma parameters. This is not necessary, Just say we
  checked the power when the significance level is .05.}\mc{addressed}
We can compute a rejection rate 
at a nominal significance level of 0.05.
Additionally, we can construct a 95\% confidence interval for 
this rate. Below are tables containing rejection rates showcasing the 
differences when simulation settings are changed.

@@

Using the \textsl{tseries} package  \citep{tseries}, 
we gathered daily closing prices for the S\&P 500 index from January 1st, 2020
to December 31st, 2023. Daily returns were obtained by taking the difference in
the logarithm of the closing prices. The Kendall's $\tau$ for the series
was about -0.0298, indicating a very slight serial dependence.
Using our method, we tested that the daily returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
We tested the same hypotheses using \citet{babu2004goodness}'s 
non-parametric basic bootstrap bias correction and 
\citet{zeimbekakis2022misuses}'s parametric bootstrap method.
We used $B = 10,000$ bootstrap 
replicates in this analysis.
The p-values for these tests are highlighted in 
Table~\ref{table:SP5004}.

@@

@@
